SMT-Boosted Security Types for Low-Level MPC

### 2024-10-14 esop25/examples.tex
checkpoint

Using the Satisfiability Modulo Fields theory in cvc5 on an Apple M1
processor, we have verified correctness of additive sharing protocols
in fields up to size $\fieldp{2^{31} - 1}$ (an approximation of 32-bit
integers) which takes ~16ms to compute for 3 parties and not
significantly more than for, e.g., $\fieldp{2}$. We have also verified
the semi-homorphic encryption properties leveraged in the BDOZ circuit
library functions (Figures \ref{fig-bdozsum} and \ref{fig-bdozmult}) in
fields up to size $\fieldp{2^{31} - 1}$ which takes \cnote{TBD}ms for the
property used for the postcondition of the $\ttt{mult}$ gate. This is
categorically better performance than could be achieved using previous
brute-force methods in $\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

As for $\ttt{\_sum}$, the postcondition of the $\ttt{\_mult1}$
function expresses the relevant semi-homorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. The precondition that
input shares must possess this property is enforced by the two calls
to $\ttt{sum}$ within the body of $\ttt{mult}$ and need not be made
explicit. Finally, the postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate.

>>>>

Using the Satisfiability Modulo Fields theory in cvc5 on an Apple M1
processor, we have verified correctness of additive sharing protocols
in fields up to size $\fieldp{2^{31} - 1}$ (an approximation of 32-bit
integers) which takes ~7ms to compute for 3 parties and not
significantly more than for, e.g., $\fieldp{2}$. We have also verified
the semi-homorphic encryption properties leveraged in the BDOZ circuit
library functions (Figures \ref{fig-bdozsum} and \ref{fig-bdozmult}) in
fields up to size $\fieldp{2^{31} - 1}$ which take ~8ms for the
property used for the postcondition of the $\ttt{mult}$ gate. This is
categorically better performance than can be achieved using previous
brute-force methods in $\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

As for $\ttt{\_sum}$, the postcondition of the $\ttt{\_mult1}$
function expresses the relevant semi-homorphic encryption property of
the resulting share, MAC, and key after gate execution-- specifically,
it preserves the BDOZ authentication property. The precondition that
input shares must possess this property is enforced by the two calls
to $\ttt{sum}$ within the body of $\ttt{mult}$ and need not be made
explicit. Finally, the postcondition of $\ttt{mult}$ expresses the
correctness property of the multiplication gate. In any case,
integrity of any circuit constructed from the $\ttt{sum}$ and
$\ttt{mult}$ library functions will require little MPC.
